\documentclass{article}
\usepackage{enumitem}

\begin{document}

\section*{Introduction}
In a world driven by technology and innovation, the concept of a personal AI assistant has transcended the realm of science fiction and become a tangible reality. Imagine having your own digital companion, just like Tony Stark's Jarvis from the Iron Man series, at your beck and call. This ambitious project aims to bring that vision to life by harnessing the power of open-source software, specifically OpenCV and OpenAI.

\section*{Project Overview}
Our project revolves around the development of an AI assistant that seamlessly integrates a multitude of cutting-edge technologies to provide a truly immersive and interactive experience. Here's an overview of the core components:

\begin{enumerate}[label=\arabic*.]
  \item \textbf{Hand Tracking:} We'll employ OpenCV's hand tracking capabilities to enable intuitive and natural interaction with the AI assistant through hand gestures. Users can control and navigate the assistant's interface with simple movements, enhancing the overall user experience.

  \item \textbf{Face Recognition:} Leveraging OpenCV's face recognition algorithms, our AI assistant will be able to identify and personalize interactions with different users. It can greet users by name, adjust settings according to preferences, and enhance security through facial authentication.

  \item \textbf{Body Detection:} Using advanced body detection techniques, the AI assistant will be aware of the user's presence and gestures within the environment. This enables context-aware responses and actions, making interactions more dynamic and relevant.

  \item \textbf{Voice Recognition:} Integrating OpenAI's voice recognition capabilities, our AI assistant will have the ability to understand and respond to voice commands. Users can engage in natural conversations with the assistant, enabling a wide range of tasks and queries to be executed via voice.
\end{enumerate}

\end{document}
